|

### 2023-02-06 paper.Rmd
autogit

The results for the median best fitness over the evolutionary search are visualized in figure \@ref(fig:symReg-Fitness).

@@

>>>>

The results for the median best fitness over the evolutionary search are visualized in figure \@ref(fig:symReg-Fitness). Figure \@ref(fig:symReg-Fitness-BoxPlots) shows the distribution of final fitness values on both the test and training set as boxplots.

@@

```{r symReg-Fitness-BoxPlots, echo=FALSE, fig.cap="Fitness after 30 Generations - Real World Symbolic Regression", out.width="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/final_fitness_boxplot.png")
```

### 2023-02-06 paper.tex
autogit

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2023-02-05}

@@

The results for the median best fitness over the evolutionary search are visualized in figure \ref{fig:symReg-Fitness}.

@@

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1975}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1728}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0741}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1481}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1481}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0988}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1605}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-fitness}Median Best Fitness after 30 generations - Real World Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hidden-Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Set
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hidden-Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Set
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & Train & \textbf{12.6611} & 16.2778 & 0.57 & 0.16 \\
& 1 & Test & \textbf{12.5944} & 16.2131 & 0.62 & 0.14 \\
Airfoil & 2 & Train & \textbf{7.0644} & 7.7109 & 0.62 & 0.14 \\
& 2 & Test & \textbf{6.991} & 7.6799 & 0.91 & 0.04 \\
Boston\_Housing & 2 & Train & \textbf{8.0217} & 8.0543 & 0.85 & 0.06 \\
& 2 & Test & \textbf{7.9472} & 7.9683 & 0.79 & 0.08 \\
Energy(Cooling) & 2 & Train & \textbf{4.449} & 4.4627 & 0.82 & 0.07 \\
& 2 & Test & \textbf{4.6258} & 4.6297 & 0.96 & -0.03 \\
Concrete & 2 & Train & \textbf{17.1299} & 17.9175 & 0.51 & 0.24 \\
& 2 & Test & \textbf{17.1585} & 17.6584 & 0.68 & 0.16 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2388}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1642}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1045}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1791}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1194}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1940}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-best-solution-size}Median Size of the best solution after 30 generations - Real World Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & \textbf{5} & 7 & 0.44 & 0.20 \\
Airfoil & 2 & 5 & 5 & 0.97 & -0.02 \\
Boston\_Housing & 2 & 3 & 3 & 0.37 & -0.20 \\
Energy(Cooling) & 2 & 3 & 3 & 0.16 & -0.33 \\
Concrete & 2 & 7 & \textbf{5} & 0.09* & -0.56 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2388}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1642}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1045}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1791}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1194}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1940}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-popDiversity}Median Population Diversity over 30 Generations - Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & 0.86 & \textbf{0.93} & 0.00*** & 0.93 \\
Airfoil & 1 & 0.86 & \textbf{0.93} & 0.00*** & 0.93 \\
Boston\_Housing & 1 & 0.88 & \textbf{0.95} & 0.00*** & 0.92 \\
Energy(Cooling) & 1 & 0.87 & \textbf{0.94} & 0.00*** & 0.94 \\
Concrete & 1 & 0.87 & \textbf{0.94} & 0.00*** & 0.94 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2388}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1642}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1045}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1791}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1194}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1940}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-epochsPerGen}Median Number of Training Epochs per Generation - Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & 143.49 & \textbf{64.66} & 0.00*** & -0.88 \\
Airfoil & 2 & 143.83 & \textbf{61.22} & 0.00*** & -0.88 \\
Boston\_Housing & 2 & 141.8 & \textbf{65.36} & 0.00*** & -0.87 \\
Energy(Cooling) & 2 & 144.24 & \textbf{66.81} & 0.00*** & -0.93 \\
Concrete & 2 & 139.2 & \textbf{64.21} & 0.00*** & -0.87 \\
\end{longtable}

>>>>

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2023-02-06}

@@

The results for the median best fitness over the evolutionary search are visualized in figure \ref{fig:symReg-Fitness}. Figure \ref{fig:symReg-Fitness-BoxPlots} shows the distribution of final fitness values on both the test and training set as boxplots.

@@

{\centering \includegraphics[width=0.9\linewidth]{img/symbolicRegressionSummarized/final_fitness_boxplot}

\caption{Fitness after 30 Generations - Real World Symbolic Regression}\label{fig:symReg-Fitness-BoxPlots}
\end{figure}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1975}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1728}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0741}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1481}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1481}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0988}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1605}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-fitness}Median Best Fitness after 30 generations - Real World Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hidden-Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Set
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hidden-Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Set
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & Train & \textbf{12.6611} & 16.2778 & 0.57 & 0.16 \\
& 1 & Test & \textbf{12.5944} & 16.2131 & 0.62 & 0.14 \\
Airfoil & 2 & Train & \textbf{7.0644} & 7.7109 & 0.62 & 0.14 \\
& 2 & Test & \textbf{6.991} & 7.6799 & 0.91 & 0.04 \\
Boston\_Housing & 2 & Train & \textbf{8.0217} & 8.0543 & 0.85 & 0.06 \\
& 2 & Test & \textbf{7.9472} & 7.9683 & 0.79 & 0.08 \\
Energy(Cooling) & 2 & Train & \textbf{4.449} & 4.4668 & 0.54 & 0.17 \\
& 2 & Test & \textbf{4.6258} & 4.6429 & 0.76 & 0.09 \\
Concrete & 2 & Train & 17.1299 & \textbf{16.9825} & 0.91 & -0.04 \\
& 2 & Test & 17.1585 & \textbf{16.7413} & 0.62 & -0.14 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2388}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1642}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1045}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1791}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1194}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1940}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-best-solution-size}Median Size of the best solution after 30 generations - Real World Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & \textbf{5} & 7 & 0.44 & 0.20 \\
Airfoil & 2 & 5 & 5 & 0.97 & -0.02 \\
Boston\_Housing & 2 & 3 & 3 & 0.37 & -0.20 \\
Energy(Cooling) & 2 & 3 & 3 & 0.21 & -0.28 \\
Concrete & 2 & 7 & \textbf{5} & 0.21 & -0.33 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2388}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1642}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1045}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1791}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1194}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1940}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-popDiversity}Median Population Diversity over 30 Generations - Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & 0.86 & \textbf{0.93} & 0.00*** & 0.93 \\
Airfoil & 1 & 0.86 & \textbf{0.93} & 0.00*** & 0.93 \\
Boston\_Housing & 1 & 0.88 & \textbf{0.95} & 0.00*** & 0.92 \\
Energy(Cooling) & 1 & 0.87 & \textbf{0.94} & 0.00*** & 0.94 \\
Concrete & 1 & 0.87 & \textbf{0.94} & 0.00*** & 0.93 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2388}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1642}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1045}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1791}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1194}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1940}}@{}}
\caption{\label{tab:full-run-realWorldSymReg-epochsPerGen}Median Number of Training Epochs per Generation - Symbolic Regression}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Problem
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hid.Layers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DAE-GP
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pre-Trained
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
P-Value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cliffs-Delta
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Airfoil & 1 & 143.49 & \textbf{64.66} & 0.00*** & -0.88 \\
Airfoil & 2 & 143.83 & \textbf{61.22} & 0.00*** & -0.88 \\
Boston\_Housing & 2 & 141.8 & \textbf{65.36} & 0.00*** & -0.87 \\
Energy(Cooling) & 2 & 144.24 & \textbf{66.7} & 0.00*** & -0.93 \\
Concrete & 2 & 139.2 & \textbf{65.15} & 0.00*** & -0.87 \\
\end{longtable}
